---
title: "p8105_hw6_sl5232"
author: "Shangsi Lin"
date: "`r Sys.Date()`"
output: html_document
---
## Homework 6
```{r setup, include=FALSE}
library(tidyverse)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

```{r load_libraries}
library(tidyverse)
library(modelr)
```

### Problem 1

To obtain a distribution for $\hat{r}^2$, we'll follow basically the same procedure we used for regression coefficients: draw bootstrap samples; the a model to each; extract the value I'm concerned with; and summarize. Here, we'll use `modelr::bootstrap` to draw the samples and `broom::glance` to produce `r.squared` values. 

```{r weather_df, cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  ggplot(aes(x = r.squared)) + geom_density()
```

In this example, the $\hat{r}^2$ value is high, and the upper bound at 1 may be a cause for the generally skewed shape of the distribution. If we wanted to construct a confidence interval for $R^2$, we could take the 2.5% and 97.5% quantiles of the estimates across bootstrap samples. However, because the shape isn't symmetric, using the mean +/- 1.96 times the standard error probably wouldn't work well.

We can produce a distribution for $\log(\beta_0 * \beta1)$ using a similar approach, with a bit more wrangling before we make our plot.

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(id = `.id`, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate) %>% 
  rename(beta0 = `(Intercept)`, beta1 = tmin) %>% 
  mutate(log_b0b1 = log(beta0 * beta1)) %>% 
  ggplot(aes(x = log_b0b1)) + geom_density()
```

As with $r^2$, this distribution is somewhat skewed and has some outliers. 

The point of this is not to say you should always use the bootstrap -- it's possible to establish "large sample" distributions for strange parameters / values / summaries in a lot of cases, and those are great to have. But it is helpful to know that there's a way to do inference even in tough cases. 

### Problem 2
Download the interested data from github and store it in the data file. Then create a `city_state` variable and a binary variable indicating whether the homicide is solved. Omit cities that don't report victim race and Tulsa, AL, which is a data entry mistake. Due to our interest, limit the analysis on `victim_race` is white or black. Set `victim_age` to be numeric.

```{r}
homicide_df = read_csv("data/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(city_state = str_c(city, ", ", state)) %>% 
  mutate(solved = as.numeric(disposition == "Closed by arrest")) %>% 
  filter(city_state != "Dallas, TX", city_state != "Phoenix, AZ", city_state != "Kansas City, MO", city_state != "Tulsa, AL") %>% 
  filter(victim_race == "White" | victim_race == "Black") %>% 
  filter(victim_age != "Unknown") %>% 
  mutate(victim_age = as.numeric(victim_age))
```

For the city of Baltimore, use the `glm` function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex, and race as predictors. Save the output of `glm` as an R object and  apply `broom::tidy` to this object. Obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed. 

```{r}
LR_Baltimore = homicide_df %>% 
  filter(city_state == "Baltimore, MD") %>% 
  glm(solved ~ victim_age + victim_sex + victim_race, data=., family = binomial())

save(LR_Baltimore, file = "results/LR_Baltimore.RData")

LR_Baltimore %>% 
  broom::tidy() %>% 
  mutate(lower_ci = confint(LR_Baltimore)[,1], upper_ci = confint(LR_Baltimore)[,2]) %>% 
  mutate(odds_ratio = exp(estimate), lower_ci = exp(lower_ci), upper_ci = exp(upper_ci))
  
```

According to our extracted estimate and confidence interval of the adjusted odds ratio above, in the city of Baltimore, MD, the male victims has about the half of the odds of getting a solved case compared to the female victims, with an point estimate of 0.426 the odds to be exact.

Next, run `glm` for each of the cities in the dataset, and extract the adjusted odds ratio and CI for solving homicides comparing male victims to female victims. Create a dataframe with estimated ORs and CIs for each city.

```{r}
ORCI_cities = homicide_df %>% 
  select(city_state, victim_race:victim_sex, solved) %>% 
  nest(victim_info = victim_race:solved) %>% 
  mutate(LR_cities = map(victim_info, ~glm(solved ~ victim_age + victim_sex + victim_race, family= binomial, data=.x)),
    results = map(LR_cities, broom::tidy),
    ci = map(LR_cities, ~confint(.x,"victim_sexMale"))) %>% 
  select(city_state,results,ci) %>% 
  unnest(results) %>% 
  filter(term == "victim_sexMale") %>% 
  unnest_wider(ci) %>% 
  mutate(estimate = exp(estimate), `2.5 %` = exp(`2.5 %`), `97.5 %` = exp(`97.5 %`)) %>% 
  select(city_state, estimate, `2.5 %`, `97.5 %`)
```

Lastly, create a plot that shows the estimated ORs and CIs for each city, organize cities according to estimated OR.

```{r}
ORCI_cities %>% 
  ggplot(aes(x = fct_reorder(city_state, estimate), y = estimate)) + 
  geom_point() +
  geom_errorbar(aes(ymin = `2.5 %`, ymax = `97.5 %`)) +
  labs(title = "Male vs. Female victims adjusted odds ratio estimate for solved homicides across America") + xlab("City, State") + ylab("Estimated Odds Ratio") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

From the produced plot we can see that New York has the lowest male vs. female victim adjusted odds ratio estimate for solved homicides, which is about 0.25, while Albuquerque has the highest odds ratio estimate at about 1.75. It is also worth to note that among the 47 cities included in this plot, most cities has an odds ratio between 0.25 to 1. While the only three cities with odds ratio significantly above 1 also has significantly larger confidence intervals.

### Problem 3

This problem investigates on the effects of several variables on a child's birthweight. First load and clean the data for regression analysis.

```{r}
birthweight = read_csv("data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(babysex = recode(babysex, `1` = "Male", `2` = "Female"),
         frace = recode(frace, `1` = "White", `2` = "Black", `3` = "Asian", `4` = "Puerto Rican", `8` = "Other", `9` = "Unknown"),
         mrace = recode(mrace, `1` = "White", `2` = "Black", `3` = "Asian", `4` = "Puerto Rican", `8` = "Other")) %>% 
  drop_na()
```

